# imageFilter 📸🎨

Using the' magick' package, an R package is used to apply custom image filters.

## ✨ Features

-   Convert images to grayscale
-   Apply a magenta/black cutoff filter
-   Easily extendable to add more custom pixel-level filters

## 📦 Installation

You can install the development version of `ImageFilters` from your local directory using:

```{r}
# if you haven't yet:

install.packages("devtools")

# install the package (adjust the path)

devtools::install_github("https://github.com/darck3/imageFilter1.5/tree/main")

```

##Requirements

```{r}
install.packages("magick")
```

##Usage

```{r}
library(imageFilter)
library(magick)

# Read an image

img <- image_read("path/to/your/image.jpg")

# Convert to bitmap

bitmap <- img[[1]]

# Apply grayscale filter

gray_img <- apply_filter(bitmap, greyscale_filter)
print(gray_img)

# Apply cutoff filter (black or magenta)

cutoff_img <- apply_filter(bitmap, cutoff_filter, cutoff = 128)
print(cutoff_img)
```

##How it works

-   apply_filter() function iterates through each pixel of an image’s bitmap and applies a user-defined filter function. Two example filters are included:

    -   greyscale_filter() – converts RGB pixels to grayscale.

    -   cutoff_filter() – assigns black or magenta based on brightness.
